\chapter{Conclusion}
\label{sec:conclusion}

We proposed Darwinian Network Library as new framework for modeling and inference in DNs.
DN library is a implementation of the basic operations for adaptation and evolution in DNs.
It is implemented with the Python programming language and the basic data structures are provided by Darwin library.
%It provides salient features as test unity and a tutorials with IPython Notebook.
The main advantage of the DN library is to apply novel ideas and techniques of DNs.
DN library also is great for teaching, quick prototyping with DNs and testing.


DN library is based upon the novel library Darwin, a Python framework for BN modeling and inference.
Darwin library has two main categories called potentials and graph manipulations.
The former is a data structure for modeling a probability table.
The latter maps nodes in the graph to a list of potentials.
Together they form a reliable structure to reason on BNs.

We have established in Chapter \ref{sec:dn_lib} features of DN library given the manipulation tools from Darwin.
We have shown that DN library is an intuitive framework for working with DNs.
For instance, to build a set of potentials, one can simply utilize the class \emph{Population}.
Intuitively, with objects \emph{Population} together we can obtain a class \emph{DarwinianNetwork}.

Another salient feature is the set of procedures for drawing Populations and DarwinianNetworks.
It allows the user to see how looks like a population that has just been created - or even the entire DN!


This project proposes the implementation of a DN library.
In summary, we have stablished four main advantages of using DN library:
\begin{inparaenum}[(i)]
\item due its simple approach given the Python implementation, it has an expressive language that facilitate its usage;
\item it has interactive visual tools to compute and draw DNs, enabling users to better interact with the library;
\item it is a great tool for learning and its operations are sound given the unit tests;
\item and all source code is available free online on \emph{GitHub} through the webpage:
\end{inparaenum}
\begin{center}
\url{https://github.com/Darwinian-Networks}
\end{center}
With DN library, DNs can be applied as the simple and yet remarkably robust tool they are, allowing users to simplify reasoning with BNs.
